A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-16 paper.tex
added an abstract, more small additions

\title{Twists of Supersymmetric Gauge Theories}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

@@

\begin{abstract}

\end{abstract}

@@

Note that the supertranslation Lie algebra $\fA$ is a $\Spin(V_\RR)\times G_R$-equivariant super Lie algebra.

@@

\subsection{Supersymmetric Twisting}
The idea of twisting, originally developed by Witten \chris{refs}, is \chris{todo: brief contextual remarks, not much detail, as we'll say more in the intro.}

@@

Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.  This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.  We have a natural embedding
\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
\[G_W = G_V\times \Spin(W^\perp_\RR).\]
This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ \chris{we never actually defined supersymmetry algebras or R-symmetry: need to go back and add this to Section \ref{sec:susyalgebras}.}.

@@

\begin{comment}
\pavel{This might go in the coupling section.}
We can deduce supersymmetry for other super Yang-Mills theories using dimensional reduction, specifically Proposition \ref{dim_red_SUSY_prop}.
\begin{corollary}
Let $n$ be one of the special dimensions $3,4,6$ or 10, and choose $m < n$.  Let $\Sigma'$ be the $\so(m)$ representation obtained by restriction of the $\so(n)$ representation $\Sigma$.  Then the super Poincar\'e algebra
\[\mf A' = \mf{iso}(m) \oplus \Pi \Sigma',\]
obtained by restricting the $n$-dimensional super Poincar\'e algebra associated to $\Sigma$, acts on the $m$-dimensional super Yang-Mills theory $\mf L'$ with matter representation $\Sigma'$.
\end{corollary}

\begin{proof}
This follows immediately by applying Proposition \ref{dim_red_SUSY_prop} to the $\mf A$-supersymmetric theory $\mf L$ on $\RR^n$.
\end{proof}

\begin{remark}
We can further include the action of at least a subalgebra of the algebra of R-symmetries in each example. \chris{quantify which}
\end{remark}
\end{comment}

@@

\item $A_\RR=\mathbb{H}$, so $A=\eend(Z)$. A left $A$-module is necessarily of the form $P\cong W_+\otimes U$, where $A$ just acts on $Z$. Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $Z$ and a symplectic pairing on $U$. So, the data boils down a symplectic $\fg$-representation $U$.
\end{itemize}

@@

\section{Dimension 8}
\vspace{-10pt}
\paragraph{Fields:} 
The 8-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^8$.  It has BRST fields given by a ghost $c$ along with the following.
\begin{itemize}
 \item Bosons: an 8d gauge field $A$ in $\Omega^1(\RR^8; \gg)$, and a pair of $\gg$-valued scalar fields $\phi_1$ and $\wt \phi_1$ in $\Omega^0(\RR^8; \gg)$.
 \item Fermions: a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in \Omega^0(\RR^8; \gg \otimes(S_+ \oplus S_-))$.
\end{itemize}

@@

\section{Dimension 7} \label{7d_section}
The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.  It has BRST fields given by a ghost, a 7d gauge field $A$, three $\gg$-valued scalar fields $\phi_1$, $\phi_2$ and $\phi_3$, and a symplectic Dirac spinor field $\lambda$ in $S \otimes W$, where $W$ is a 2-dimensional symplectic vector space.

@@

The following equivalences follow from the results in the previous section by substituting $R = $ \chris{what is it exactly?}.

>>>>

\title{A Catalogue of Twists of Supersymmetric Gauge Theories}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

@@

\begin{abstract}
We give a complete classification of supersymmetric twists of super Yang-Mills theories with matter in all dimensions.  Super Yang-Mills theories can be modelled classically using the BV formalism; we construct the supersymmetry algebra action using the language of $L_\infty$ algebras, then for each class of square-zero supercharge we give a description of the corresponding twisted theory in terms of partially holomorphic versions of Chern-Simons and BF theory. 
\end{abstract}

@@

Note that the supertranslation Lie algebra $\fA$ is a $\Spin(V_\RR)\times G_R$-equivariant super Lie algebra.  We will sometimes want to refer to the infinitesimal version of this action.
\begin{definition}
Let $\fA$ be a supertranslation algebra.  The corresponding \emph{supersymmetry algebra} is the Lie algebra $(\so(V) \oplus \gg_R) \ltimes \fA$.
\end{definition}

@@

\subsection{Supersymmetric Twisting}
The idea of twisting, originally developed by Witten \cite{WittenTQFT}, is to modify a classical BV theory by deforming the differential $Q_{\mr{BV}}$ by the action of a square-zero fermionic symmetry.

@@

Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.  This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.  We have a natural embedding
\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
\[G_W = G_V\times \Spin(W^\perp_\RR).\]
This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ as defined in Section \ref{sec:susyalgebras}.

@@

@@

\item $A_\RR=\mathbb{H}$, so $A=\eend(W_+)$. A left $A$-module is necessarily of the form $P\cong W_+\otimes U$, where $A$ just acts on $W_+$. Compatibility of the orthogonal pairing on $P$ with the $A$-action implies that it is given by a product of the symplectic pairing on $W_+$ and a symplectic pairing on $U$. So, the data boils down a symplectic $\fg$-representation $U$.
\end{itemize}

@@

\section{Dimension 8}

\vspace{-10pt}
\paragraph{Fields:} 
The 8-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^8$.  It has BRST fields given by a ghost $c$ along with the following.
\begin{itemize}
 \item Bosons: an 8d gauge field $A$ in $\Omega^1(\RR^8; \gg)$, and a pair of $\gg$-valued scalar fields $\phi_1$ and $\wt \phi_1$ in $\Omega^0(\RR^8; \gg)$.
 \item Fermions: a Dirac spinor field $\lambda = (\lambda_+, \lambda_-) \in \Omega^0(\RR^8; \gg \otimes(S_+ \oplus S_-))$.
\end{itemize}

@@

\section{Dimension 7} \label{7d_section}

\subsection{\texorpdfstring{$\cN=1$}{N=1} super Yang--Mills theory}
The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.  It has BRST fields given by a ghost, a 7d gauge field $A$, three $\gg$-valued scalar fields $\phi_1$, $\phi_2$ and $\phi_3$, and a symplectic Dirac spinor field $\lambda$ in $S \otimes W$, where $W$ is a 2-dimensional symplectic vector space.

@@

The following equivalences follow from the results in the previous section by substituting $R = U \oplus \gg$.
